Recpature distances

### 2024-05-13 recaptureanalysis/recaps.Rmd
zooplankton stuff

>>>>

#put brood year on the x-axis?
ggplot(releasestat, aes(x = as.factor(BroodYear), y = RecapRate*100, fill = as.factor(BroodYear)))+
  geom_boxplot()+
  facet_wrap(~FFyn)+
  ylab("Percentage Recaptured")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust =1, vjust =1),
        legend.position = "none")+
  xlab(NULL)

#facet by brood year
ggplot(releasestat, aes(x = Type2, y = RecapRate*100, fill = Type2))+
  geom_boxplot()+
  facet_grid(BroodYear~FFyn)+
  ylab("Percentage Recaptured")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust =1, vjust =1),
        legend.position = "none")+
  xlab(NULL)
